---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# countingMissings

<!-- badges: start -->
<!-- badges: end -->

This package contains a function to count missing values for all columns by group. By passing the data frame or tibble and columns to group by, this function will return a data frame or tibble with the number of NAs in each group specified in parameters. You can also pass the optional parameter ".group" to specify whether to keep the output data frame grouped by groups.

The dependency is the dplyr library.

## Installation

You can install the development version of countingMissings from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/countingMissings")
```

## Example

This example computes the number of missing values in the `airquality` dataset grouped by the `cyl` column. 

```{r example}
library(countingMissings)
count_all_missing_by_group(airquality, Month)
```

This example has the same output as the last example, but shows off an alternative way of invoking the `count_all_missing_by_group()`: piping the dataset into the function. 

```{r cars}
airquality |> count_all_missing_by_group(Month) 
```

The optional `.groups` argument allows us to keep the output grouped by the grouping column. See example below; notice how the output is a grouped tibble, rather than the ungrouped tibble output of the earlier examples. 

```{r pressure, echo = FALSE}
count_all_missing_by_group(airquality, Month, .groups = "keep")
```

